---
title: "Comparing stm to traditional LDA"
output:
  html_document:
    df_print: paged
---

I want to begin by importing data that already has cleaned text, lots of possible co-variates, and has been fitted with an LDA model using gensim in python. I'll then fit a new LDA using the stm package, then a SAGE model without co-variates, and then a SAGE model with covariates

```{r load libraries}
library(stm) # runs the topic models
library(quanteda) # makes the dictionary and corpus
library(tidyverse) # makes nice output and stuff
library(tidytext) # does amazing things with text
library(drlib) # for reorder within
library(tidystm)
```


```{r read data}
cl_train <- read_csv('data/no_dupes_lda_fit5_26.csv') %>% #read python LDA data
  rename(py_index = X1) %>% # rename the old index column (starts at 0)
  rename_at(vars(`0`:`9`), funs(paste0('topic_',.))) %>% # rename the topics by prepending 'topic'
  mutate( # add some new variables for regressions
    pop_thousands = total_RE/1000, # population in thousands
    percent_white = white_proportion*100, # racial percentages
    percent_black = black_proportion*100)

```



# Training a SAGE stm with covariates
```{r fit SAGE stm}
temp<- textProcessor(documents = cl_train$clean_text, metadata=cl_train)
out <- prepDocuments(temp$documents, temp$vocab, temp$meta)
sage_model_12 <- stm(out$documents, out$vocab, K = 12, prevalence = ~high_black + high_white + pop_thousands + log_income + log_price, data=out$meta)
sage_model_all_race <- stm(out$documents, out$vocab, K = 24, prevalence = ~black_proportion + white_proportion + latinx_proportion + asian_proportion + pop_thousands + log_income + log_price, data=out$meta) # fit an SAGE model using stm and covariates

K = c(16,18,20,22,24,26,28,30)
search_results = searchK(out$documents, out$vocab, K = K, prevalence = ~white_proportion + black_proportion + pop_thousands + log_income + log_price, data=out$meta)
search_results
plot(search_results)
labelTopics(sage_model_12)
cl_train %>% select(high_white, high_black, income, clean_price, pop_thousands) %>% summarise_all(sd)
data.frame(t(summary_stats))
```


Very high correlations are still common with the SAGE model. 
SAGE and LDA models as estimated by stm are very highly correlated

```{r t tests}
#td_gamma <- tidy(sage_model_12, matrix = "gamma") # get topic proprtions by document
#sage_2_fit <- spread(td_gamma,topic,gamma) %>% mutate(document = out$meta$postid) # spread the proportions

cl_merged <- cl_train %>% select(postid, high_white, high_black, black_proportion, white_proportion, log_income, log_price, pop_thousands, listingText, body_text, clean_text, clean_price, address, postid, GEOID10) %>% mutate(postid=as.character(postid)) %>% inner_join(sage_2_fit %>% mutate(document = as.character(document)), by=c('postid'='document')) # merge with gensim lda
high_prop = cl_merged %>% filter(high_white==1) %>% select(`1`:`12`) %>% as.data.frame() # make a df limited to one set of a stratifier
low_prop = cl_merged %>% filter(high_white==0) %>% select(`1`:`12`) %>% as.data.frame() # an the other side
labels <- sageLabels(sage_model) #extract model labels

ttest_out <- function(a,b){ # output and save parts of the t.test function
  test <- t.test(a,b, alternative = 'two.sided', conf.level = 0.95) # set params
  p <- test$p.value #save p value
  point_est <- test$estimate[1] - test$estimate[2] # save point estimate
  high_est <- max(test$conf.int) # save the high estimate
  low_est <- min(test$conf.int) # and the low estimate
  return(data_frame('point_est' = point_est, 'high_est' = high_est, 'low_est' = low_est, 'p_value'=p)) # return a tibble row
}

tmp = data_frame() # start with an empty dataframe
for(i in 1:12){ # loop through topics
  tmp = bind_rows(tmp, ttest_out(high_prop[,i] ,low_prop[,i])) #t.test each row
}
t_tests <- bind_cols(tmp, 'topic' = names(high_prop)) %>% # add a row of topic names
  select(topic, everything()) %>% # reoder cols
  mutate(topic = gsub('_',' ',topic), topic = gsub('t','T',topic)) # make nice names
t_tests %>% arrange(desc(abs(point_est))) # uncomment to show t_tests
```

```{r rope ladder}
# make rope ladder plot of output
t_tests %>% # retain only large mean differences
  ggplot(aes(x = reorder(topic,-point_est), y = point_est)) + # reorder topics for pretty output
    geom_pointrange(aes(ymax = high_est, ymin = low_est), color = "darkblue") + # plot the rope ladder
    geom_text(aes(label = round(point_est,4)), nudge_x = 0.2) + # add point estimates
    #geom_text(aes(label = topic, nudge_x = -.2)) + # add topic names
    scale_x_discrete("") + # remove x label and scale
    geom_hline(yintercept = 0, color = "red") + # plot a line at 0
    theme_minimal() + # auto exlude backgound shading
    theme(text = element_text(size=10))+ #, # set values for text
          #axis.text.y = element_blank()) + #remove y text
    ylab('Topic prevalant in low White neighborhoods          Topic prevalant in high White neighborhoods')+ # label the high and low proportions
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    coord_flip()+ # remove gridlines
    ggtitle("Comparison of Mean Differences Between High White and Low White Neighborhoods") # set title
```

```{r}
#topicQuality(sage_model_12, out$documents)
effects <- estimateEffect(1:26 ~ black_proportion + asian_proportion + latinx_proportion + pop_thousands + log_income + log_price, sage_model, out$meta)
effects_dummies <- estimateEffect(1:26~white_proportion + black_proportion + pop_thousands + log_income + log_price, sage_model_dummies, out$meta)
effects_12 <- estimateEffect(1:12 ~ high_white, sage_model_12, out$meta)
effects_full <- estimateEffect(1:24 ~ black_proportion + white_proportion + latinx_proportion + asian_proportion + pop_thousands + log_income + log_price, sage_model_all_race, out$meta)
effects_black <- estimateEffect(1:12 ~ h + pop_thousands + log_income + log_price, sage_model_all, out$meta)
sum <- summary(effects_12)
plot(effects_12, "log_price", method = 'difference', cov.value1 =7.3, cov.value2 = 7.8)
summary(effects_white)
summary(effects_latinx)
summary(effects_full)
sum
```

```{r}
topic_titles = c('Rent-by-owner',
'New Central Neighborhood',
'Developments: Social Community',
'Developments: Car friendly',
'Expensive Single Family Homes',
'Core Neighborhoods, Basic Units',
'Luxury Hipster Apartments',
'Downtown with views',
'Response to Ordinances',
'Developments: Out of town',
'Excellent Schools ',
"'In the heart of' core neighborhoods")

```


```{r}
coef_sum <- data.frame()
for(i in 1:12){
  row <- data.frame(topic = paste('Topic',i),
                    title = topic_titles[[i]],
                    race = c('white','black'),
                    coefs = c(sum$tables[i][[1]][2,1],sum$tables[i][[1]][3,1]), 
                    stderrs = c(sum$tables[i][[1]][2,2],sum$tables[i][[1]][3,2])
                    )
  coef_sum <- bind_rows(coef_sum, row)
}
coef_sum %>% mutate(high_est = coefs + stderrs, low_est = coefs - stderrs, topic = factor(topic)) %>% filter(race=='black') %>%
  ggplot(aes(x = reorder(topic, -coefs), y = coefs))+
    geom_hline(yintercept = 0, color = "red", alpha=.5) + # plot a line at 0
    geom_pointrange(aes(ymax = high_est, ymin = low_est), color = 'purple')+
    geom_text(aes(y = coefs + (.0009*nchar(title)), label = title)) +
    geom_text(aes(label = topic), nudge_y = -.009) +
    theme_minimal() + # auto exlude backgound shading
    theme(text = element_text(size=10))+ #, # set values for text
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    ggtitle("Estimated Effects of high-Black neighborhoods on Topic Distributions")+
    theme(text = element_text(size=10), #, # set values for text
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    ylim(-.04,.075)+
    coord_flip() # remove gridlines

coef_sum %>% mutate(high_est = coefs + stderrs, low_est = coefs - stderrs, topic = factor(topic)) %>% filter(race=='white') %>%
  ggplot(aes(x = reorder(topic, -coefs), y = coefs))+
    geom_hline(yintercept = 0, color = "red", alpha=.5) + # plot a line at 0
    geom_pointrange(aes(ymax = high_est, ymin = low_est), color='darkblue')+
    geom_text(aes(y = coefs + (.0021*nchar(title)), label = title)) +
    geom_text(aes(label = topic), nudge_y = -.017) +
    theme_minimal() + # auto exlude backgound shading
    theme(text = element_text(size=10))+ #, # set values for text
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    ggtitle("Estimated Effects of high-White neighborhoods on Topic Distributions")+
    theme(text = element_text(size=10), #, # set values for text
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    ylim(-.09,.21)+
    coord_flip() # remove gridlines

length(coef_sum$title[[1]])
```

```{r}
coef_sum %>% mutate(high_est = coefs + stderrs, low_est = coefs - stderrs, topic = factor(topic)) %>% filter(race=='black') %>%
  ggplot(aes(x = reorder(topic, -coefs), y = coefs))+
    geom_hline(yintercept = 0, color = "red", alpha=.5) + # plot a line at 0
    geom_pointrange(aes(ymax = high_est, ymin = low_est), color = 'purple')+
    #geom_text(aes(y = coefs + (.0009*nchar(title)), label = title)) +
    geom_text(aes(label = topic), nudge_y = -.007) +
    theme_minimal() + # auto exlude backgound shading
    theme(text = element_text(size=10))+ #, # set values for text
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    ggtitle("Estimated Effects of high-Black neighborhoods on Topic Distributions")+
    theme(text = element_text(size=10), #, # set values for text
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +# remove gridlines
    #ylim(-.04,.075)+
    coord_flip()

coef_sum %>% mutate(high_est = coefs + stderrs, low_est = coefs - stderrs, topic = factor(topic)) %>% filter(race=='white') %>%
  ggplot(aes(x = reorder(topic, -coefs), y = coefs))+
    geom_hline(yintercept = 0, color = "red", alpha=.5) + # plot a line at 0
    geom_pointrange(aes(ymax = high_est, ymin = low_est), color='darkblue')+
    #geom_text(aes(y = coefs + (.0021*nchar(title)), label = title)) +
    geom_text(aes(label = topic), nudge_y = -.011) +
    theme_minimal() + # auto exlude backgound shading
    theme(text = element_text(size=10))+ #, # set values for text
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    ggtitle("Estimated Effects of high-White neighborhoods on Topic Distributions")+
    theme(text = element_text(size=10), #, # set values for text
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
   # ylim(-.09,.21)+
    coord_flip() # remove gridlines

```

```{r}
coef_sum %>% mutate(high_est = coefs + stderrs, low_est = coefs - stderrs, topic = factor(topic)) %>% filter(race=='black') %>%arrange(desc(abs(coefs))) %>% head(5) %>%
  ggplot(aes(x = reorder(topic, -coefs), y = coefs))+
    geom_hline(yintercept = 0, color = "red", alpha=.5) + # plot a line at 0
    geom_pointrange(aes(ymax = high_est, ymin = low_est), color = 'purple')+
    geom_text(aes(y = coefs + (.001*nchar(title)), label = title)) +
    geom_text(aes(label = topic), nudge_y = -.009) +
    theme_minimal() + # auto exlude backgound shading
    theme(text = element_text(size=10))+ #, # set values for text
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    ggtitle("Top 5 Largest high-Black effects")+
    theme(text = element_text(size=10), #, # set values for text
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    ylim(-.04,.065)+
    coord_flip() # remove gridlines

coef_sum %>% mutate(high_est = coefs + stderrs, low_est = coefs - stderrs, topic = factor(topic)) %>% filter(race=='white') %>% arrange(desc(abs(coefs))) %>% head(5) %>%
  ggplot(aes(x = reorder(topic, -coefs), y = coefs))+
    geom_hline(yintercept = 0, color = "red", alpha=.5) + # plot a line at 0
    geom_pointrange(aes(ymax = high_est, ymin = low_est), color='darkblue')+
    geom_text(aes(y = coefs + (.0021*nchar(title)), label = title)) +
    geom_text(aes(label = topic), nudge_y = -.017) +
    theme_minimal() + # auto exlude backgound shading
    theme(text = element_text(size=10))+ #, # set values for text
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    ggtitle("Top 5 Largest high-White effects")+
    theme(text = element_text(size=10), #, # set values for text
          axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    ylim(-.09,.21)+
    coord_flip() # remove gridlines

```

```{r}
write_csv(cl_merged, 'data/stm_twelve_5_29.csv')
cl_merged %>% names() 

cl_merged %>% filter(high_black==0) %>% filter(str_detect(body_text,"security")) %>% select(body_text, `1`:`12`, everything())
cl_merged %>% group_by(high_black) %>% select(`1`:`12`) %>% summarise_all(mean)
```

